Circumnuclear Media and Accretion Rates of Quiescent Supermassive Black Holes

### 2015-03-29 be.tex
more general relationship for zeta_crit.

For cusp galaxies ($\Gamma$=0.8), $\zeta_c\simeq \sqrt 2$
($v_w\simeq\sigma_0$).  On the other hand for core galaxies
($\Gamma$=0.1, $\delta$=1.1) we find $\zeta_c\simeq
(\rb/\rsoi)^{0.44}$, see the top panel of Fig.~\ref{fig:zetaCrit}. For
values of $\zeta<\zeta_c$, the stagnation radius rapidly approaches
the break radius as shown in the bottom panel of
Fig.~\ref{fig:zetaCrit}.
% We also find that for core galaxies for $\zeta<\zeta_c$, there is a minimum
% for $\rs/\rsoi$, $\left(\rs/\rsoi\right)_{\rm min}$--if $\rs/\rsoi$ were
% less than this value the gas enthalpy would become negative inside of
% the break radius which is clearly unphysical.  This may be roughly
% approximated using (see Fig.~\ref{fig:rbRinf})

>>>>

For cusp galaxies ($\Gamma$=0.8), $\zeta_c\simeq \sqrt 2$
($v_w\simeq\sigma_0$).  On the other hand for core galaxies
($\Gamma$=0, $\delta$=1) we find $\zeta_c\simeq
(\rb/\rsoi)^{0.5}$. More generally, we find $\zeta_c\sim
(\rb/\rsoi)^{0.5(1-\Gamma)}$ (see the top panel of
Fig.~\ref{fig:zetaCrit}).  For values of $\zeta<\zeta_c$, the
stagnation radius rapidly approaches the break radius as shown in the
bottom panel of Fig.~\ref{fig:zetaCrit}.
% We also find that for core galaxies for $\zeta<\zeta_c$, there is a minimum
% for $\rs/\rsoi$, $\left(\rs/\rsoi\right)_{\rm min}$--if $\rs/\rsoi$ were
% less than this value the gas enthalpy would become negative inside of
% the break radius which is clearly unphysical.  This may be roughly
% approximated using (see Fig.~\ref{fig:rbRinf})
